TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
revise

@@

@@

@@

@@

@@

@@

@@

>>>>

```
# SOAL 15.2

@@

# koefisien polinomial
c = np.array([6,0,0,0,0,3])
print ("Coefficient list")
print (c)

@@

# save ke dalam csv
# memberikan nama file
f = open("15_2.csv","w+")

@@

# menggambar dan menyimpan plot
plt.figure(figsize = (16,9))
plt.plot(x,y,'o-')
plt.xlabel('x')
plt.ylabel('y')
plt.savefig('15_2.png',dpi = 250)
```

@@

```
programnya
```

@@

```{r out.width = "100%",echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.3"}
knitr::include_graphics("15_3.png")
```

@@

```{r,echo=FALSE}
data = read.csv("15_3.csv")
colnames(data) = c("j","x[j]","y[j]")
data
```

@@

```
The roots:
